---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/poissonconsulting/ranmrdata.svg?branch=master)](https://travis-ci.org/poissonconsulting/ranmrdata)
[![DOI](https://zenodo.org/badge/doi/10.5281/zenodo.45222.svg)](http://dx.doi.org/10.5281/zenodo.45222)

# Loch Rannoch Ferox Trout Mark-Recapture Data 

`ranmrdata` is the companion R data package for Thorne et al.'s manuscript
The Low Abundance and High Catchability of Large Piscivorous Ferox Trout 
(Salmo trutta) in Loch Rannoch, Scotland.

## Installation

To install the package execute the following code at the R terminal:
```r
# install.packages("devtools")
devtools::install_github("poissonconsulting/ranmrdata")
```

## Information

The package provides a single tbl data frame.
```{r}
library(dplyr) # for nice printing of tbl data frames
library(ranmrdata)
ferox
```
For more information type `?ferox` at the R terminal.
